Monitoring forest health using hyperspectral imagery: Does feature selection improve the performance of machine-learning techniques?

### 2020-12-13 docs/00-manuscripts/ieee/ieee-manuscript.tex
mention the lack of multi-temporal ini-situ data

>>>>

The dataset consists of in-situ data collected within September 2016 matched against remote sensing data acquired at the end of September 2016.
A multi-temporal dataset consisting of in-situ data from different phenology stages would possibly improve the achieved model performances.
However, this would also require matching hyperspectral data of these additional timestamps.
